Squint: Lossy Hierarchical Compression on Symbol Streams

### 2012-12-06 tex/paper.tex
added parameter for controliling threshold programmatically

\subsection{Similarity vs Clustering}
For most of our benchmark tests, we focused on two extreme kinds of data:
one with large amounts of repetition at all levels, and one with a word
and sentence level structure but with little obvious large-scale repetition.
One set of test data was constructed by repeating the same letter `a' n-times
but then adding some
texture to the data by changing 1/30 of the characters uniformly
to `a'. Call these test-cases \emph{rep-n}
Another set of test data was constructed from the first n characters of the
book of Genesis from the KJV. Call these test-cases \emph{gen-n}

@@

\begin{table}[t]
\begin{tabular}{l|l|l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & C-T & C-R & C-L \\
\hline
rep-100   & 0.006 & 18/34    & 0.713 & 0.002 & 20/34    & 0.535\\
rep-400   & 0.028 & 45/76    & 0.269 & 0.009 & 41/76    & 0.743\\
rep-1600  & 0.355 & 103/194  & 0.873 & 0.042 & 103/194  & 0.804\\
rep-6400  & 3.978 & 258/448  & 0.706 & 0.203 & 256/448  & 0.869\\
rep-25600 & 135.0 & 900/1482 & 0.829 & 2.906 & 898/1482 & 0.725\\
\end{tabular}
\caption{$\epsilon = .4$}
\end{table}

\begin{table}[t]
\begin{tabular}{l|l|l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & C-T & C-R & C-L \\
\hline
rep-100   & 0.002 & 30/34    & 0.040 & 0.002 & 30/34    & 0.040\\
rep-400   & 0.019 & 60/76    & 0.035 & 0.009 & 60/76    & 0.035\\
rep-1600  & 0.350 & 123/194  & 0.355 & 0.055 & 123/194  & 0.206\\
rep-6400  & 3.942 & 280/448  & 0.387 & 0.295 & 274/448  & 0.543\\
rep-25600 & 124.5 & 922/1482 & 0.565 & 2.597 & 926/1482 & 0.437\\
\end{tabular}
\caption{$\epsilon = .2$}
\end{table}

@@

TODO: Runtime graphs and regression

@@

@@

\subsection{Larger Tests}
Final compression ratios on benchmark data
ASCII ART =p
Our Code

>>>>

\subsection{Similarity vs Clustering}
For most of our benchmark tests, we focused on two extreme kinds of data:
one with large amounts of repetition at all levels, and one with a word
and sentence level structure but with little obvious large-scale repetition.
One set of test data was constructed by repeating the same letter `a' n-times
but then adding some
texture to the data by changing 1/30 of the characters uniformly
to `*'. Call these test-cases \emph{rep-n}
Another set of test data was constructed from the first n characters of the
book of Genesis from the KJV. Call these test-cases \emph{gen-n}

@@

\begin{table}[t]
\begin{tabular}{l|l|l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & C-T & C-R & C-L \\
\hline
rep-100   & 0.006 & 18/34    & 0.713 & 0.002 & 20/34    & 0.535\\
rep-400   & 0.028 & 45/76    & 0.269 & 0.009 & 41/76    & 0.743\\
rep-1600  & 0.355 & 103/194  & 0.873 & 0.042 & 103/194  & 0.804\\
rep-6400  & 3.978 & 258/448  & 0.706 & 0.203 & 256/448  & 0.869\\
rep-12800
rep-25600 & 135.0 & 900/1482 & 0.829 & 2.906 & 898/1482 & 0.725\\
\end{tabular}
\caption{$\epsilon = .4$}
\end{table}

\begin{table}[t]
\begin{tabular}{l|l|l|l|l|l|l}
Dataset & S-T(ime) & S-R(atio) & S-L(evdistance) & C-T & C-R & C-L \\
\hline
rep-100   & 0.002 & 30/34    & 0.040 & 0.002 & 30/34    & 0.040\\
rep-400   & 0.019 & 60/76    & 0.035 & 0.009 & 60/76    & 0.035\\
rep-1600  & 0.350 & 123/194  & 0.355 & 0.055 & 123/194  & 0.206\\
rep-6400  & 3.942 & 280/448  & 0.387 & 0.295 & 274/448  & 0.543\\
rep-12800  
rep-25600 & 124.5 & 922/1482 & 0.565 & 2.597 & 926/1482 & 0.437\\
\end{tabular}
\caption{$\epsilon = .2$}
\end{table}

@@

TODO: Runtime graphs and regression. The exponents are about 1.8 and 1.3
respectively, note that the rulesize of sequitur grows at about sqrt(n)

@@

TODO: Analogous for genesis
> Growth rate for similarity is far worse for genesis

@@

\subsection{Larger Tests}
Final compression ratios on various benchmark data
ASCII ART =p
Our Code
